Papers

### 2025-04-28 papers.qmd
add patent number
add conformal paper
forgot title
add slides

## 2025
K. Goode, **J. D. Tucker**, D. Ries, and H. Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Computational Statistics and Data Analysis*, submitted, 2025. [arxiv preprint](https://arxiv.org/abs/2501.07602)

@@

## Invited Talks
"Elastic Functional Data Analsyis: with Applications to Functional Changepoint" *Stony Brook SIAM Speaker*, November 19, 2024, [Slides](https://jdtuck.github.io/presentations/StoneyBrook_Nov_24/StoneyBrook_Nov_24.html)

@@

"Method and system for training an artificial neural network utilizing physics based knowledge" US Patent No. Applied

>>>>

## 2025
J. Adams, B. Berman, J. Michalenko, **J. D. Tucker**, "Conformal Anomaly Detection for Functional Data with Elastic Distance Metrics", *arXiv:2504.01172*, submitted, 2025. [arxiv preprint](https://arxiv.org/abs/2504.01172)

K. Goode, **J. D. Tucker**, D. Ries, and H. Hoffman, "An Explainable Pipeline for Machine Learning with Functional Data", *Computational Statistics and Data Analysis*, submitted, 2025. [arxiv preprint](https://arxiv.org/abs/2501.07602)

@@

## Invited Talks
"Bayesian Model Calibration: An Elastic Appraoch" *Colorado State Univeristy Statistics Seminar*, April 28, 2025, [Slides](https://jdtuck.github.io/presentations/CSU_April25/CSU_April25.html)

"Elastic Functional Data Analsyis: with Applications to Functional Changepoint" *Stony Brook SIAM Speaker*, November 19, 2024, [Slides](https://jdtuck.github.io/presentations/StoneyBrook_Nov_24/StoneyBrook_Nov_24.html)

@@

"Method and system for training an artificial neural network utilizing physics based knowledge" US Patent No. US12229934 [PDF](Papers/US12229934.pdf)
